Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-12 manuscript/manuscript.tex
Fix exponential densities fig in manuscript

\noindent $R$ is the mean Earth radius, $T$ is the thickness of the shell ($T = R_2
- R_1$) and $b$ is a dimensionless constant that determines the variability of the
function: a higher value of $b$ increases the maximum slope of the density function.
On exponential density analysis we will use values of $b$ equal to 1, 2, 5, 10, 30
and 100, in order to cover different kind of exponential density variations, from smooth
to sharp.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/exponential-densities.pdf}
\caption{
    Exponential density functions assigned to each spherical shell in the $D$ and
    $\delta$ ratios determination.
    Each density function corresponds to a different value of $b$ on
    Eq.~\ref{eq:density-exp}.
}
\label{fig:exp-densities}
\end{figure}

>>>>

\noindent $R$ is the mean Earth radius, $T$ is the thickness of the shell ($T = R_2
- R_1$) and $b$ is a dimensionless constant that determines the variability of the
function: a higher value of $b$ increases the maximum slope of the density function.
On exponential density analysis we will use values of $b$ equal to 1, 2, 5, 10, 30
and 100, in order to cover different kind of exponential density variations, from smooth
to sharp (Fig.~\ref{fig:exp-densities}).

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]{figures/exponential-densities.pdf}
}{
\includegraphics[width=0.5\linewidth]{figures/exponential-densities.pdf}
}
\caption{
    Exponential density functions assigned to each spherical shell in the $D$ and
    $\delta$ ratios determination.
    Each density function corresponds to a different value of $b$ on
    Eq.~\ref{eq:density-exp}.
}
\label{fig:exp-densities}
\end{figure}
